Sketch of DP - Bayesian Inference

### 2018-07-08 main-sketch.tex
update abstract

\begin{abstract}
Your abstract should go here. You will also need to upload a plain-text abstract into the web submission form.
\end{abstract}

@@

\begin{figure}[ht]
\centering
\includegraphics[width=0.45\textwidth]{accuracy_vs_dimension}
\caption{Accuracy measurement based on Hellinger distance wrt. different dimensions and data size. Settings: observed data are uniformly distributed, $\epsilon = 0.8$ and $\delta = 0.00000001$, prior distributions are all $1$ in every dimension}
\label{fig_vs_dimension}
\end{figure}

@@

\begin{figure}[ht]
\centering
\includegraphics[width=0.45\textwidth]{accuracy_vs_mean_1_1}
\caption{Accuracy measurement based on Hellinger distance wrt. different data variance. Settings: $\epsilon = 0.8$ and $\delta = 0.00000001$, prior distributions are all $1$ in every dimension}
\label{fig_vs_variance}
\end{figure}

@@

\subsubsection{Accuracy Evaluation wrt. Prior Distribution and Data Variance}
\label{subsubsec_vs_prior_variance}

\begin{figure}[ht]
\centering
\includegraphics[width=0.45\textwidth]{Accuracy_VS_Prior_mean.eps}
\caption{Accuracy measurement based on Hellinger distance wrt. different prior distribution and data variances. Settings: $\epsilon = 0.8$ and $\delta = 0.00000001$, observed data sets are $[10,10,10]$ and $[1,1,28]$ and prior distributions are range from $[20,20,20]$ to $[76,76,76]$}
\label{fig_vs_prior_variance}
\end{figure}

Here, we change the prior distribution and data variance in the same time. As shown in Fig. \ref{fig_vs_prior_variance}, our exponential mechanism do better in uniform data set than in edging data set while Laplace mechanism on the contrary. Moreover, our mechanism is improving continuously and significantly as prior distribution increasing while Laplace mechanism isn't.

>>>>

\begin{abstract}
Differential privacy mechanisms now are widely used in different algorithms. Accuracy of these mechanisms is usually measured by $l_1$ norm regardless what mechanisms are based on. We observed that when mechanism protect privacy according to a certain measurement, mechanism' accuracy behavior will be better than when protect according to other measurements. This observation prompt us to design a new mechanism under Hellinger distance measurement based on basic exponential named exponential mechanism with smooth sensitivity. In this algorithm we add noise to data according to the Hellinger distance. We proved in experiments that we can have a better accuracy than Laplace mechanism which adding noise based on $l_1$ norm under Hellinger measurement.
\end{abstract}

@@

\begin{figure}[ht]
\centering
\includegraphics[width=0.45\textwidth]{accuracy_vs_dimension.eps}
\caption{Accuracy measurement based on Hellinger distance wrt. different dimensions and data size. Settings: observed data are uniformly distributed, $\epsilon = 0.8$ and $\delta = 0.00000001$, prior distributions are all $1$ in every dimension}
\label{fig_vs_dimension}
\end{figure}

@@

\begin{figure}[ht]
\centering
\includegraphics[width=0.45\textwidth]{accuracy_vs_mean_1_1.eps}
\caption{Accuracy measurement based on Hellinger distance wrt. different data variance. Settings: $\epsilon = 0.8$ and $\delta = 0.00000001$, prior distributions are all $1$ in every dimension}
\label{fig_vs_variance}
\end{figure}

@@

% \subsubsection{Accuracy Evaluation wrt. Prior Distribution and Data Variance}
% \label{subsubsec_vs_prior_variance}

% \begin{figure}[ht]
% \centering
% \includegraphics[width=0.45\textwidth]{Accuracy_VS_Prior_mean.eps}
% \caption{Accuracy measurement based on Hellinger distance wrt. different prior distribution and data variances. Settings: $\epsilon = 0.8$ and $\delta = 0.00000001$, observed data sets are $[10,10,10]$ and $[1,1,28]$ and prior distributions are range from $[20,20,20]$ to $[76,76,76]$}
% \label{fig_vs_prior_variance}
% \end{figure}

% Here, we change the prior distribution and data variance in the same time. As shown in Fig. \ref{fig_vs_prior_variance}, our exponential mechanism do better in uniform data set than in edging data set while Laplace mechanism on the contrary. Moreover, our mechanism is improving continuously and significantly as prior distribution increasing while Laplace mechanism isn't.
